### 2020-02-06 thesis/paper.tex
rel. work

VISTA \cite{VISTA} ClusterMap and user result evaluation

iVIBRATE \cite{10.1145/1148020.1148024} extension VISTA?

simple visualizations ELKI implementation \cite{10.14778/2824032.2824115}

Frameworks with specific data-sets in mind:

Propose: ``An Evolutionary and Visual Framework for Clustering of DNA Microarray Data'' \cite{DNAVis}, tool for clustering DNA data with visualization

Even Memes \cite{Dang2017}
%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{other Visual Frameworks}

>>>>

VISTA \cite{VISTA} is another visual clustering framework which was proposed by Chen and Liu and consists of three parts. Firstly, VISTA allows for data filtering which prepares data for visualization. In this step data can be normalized, missing values can be handled and if the dimensionality is to high, reduction techniques can be used. Also, if the data is to large it is possible to reduce it by extracting relevant sub-sets. Next, selecting and filtering of labels is possible. After clustering it is possible extract cluster labels for the points according to the data filtering process, allowing to for example only visualize some clusters. Lastly, the tool allows for post-processing whereby a new cluster presentation is used, which they name ClusterMap. ClusterMap projects the data on a two dimensional grid, showing the cluster labels in each cell and allowing for quick relabeling. Chen and Liu further iterate on this idea by introducing iVIBRATE \cite{10.1145/1148020.1148024} whereby they further analyze the accuracy of their tool and the theoretic background of their method.

Many clustering frameworks also implement visual elements, such that clustering results or data can be explored visually, though this often only includes trivial plots. For example the Java framework ELKI provides such simple functionality \cite{10.14778/2824032.2824115}. Generally, in most programming languages simple scatter plots and charts are available, which can be used whenever no further in-depth analysis is needed.

\subsubsection{Data-set specific Frameworks}
On to of the general frameworks for visualizing clusterings, specific ones exist that aim to better visualize the data as the framework has knowledge on the type of data.

For example, Castellanos-Garz\'{o}n and D\'{ı}az1 \cite{DNAVis} propose ``An Evolutionary and Visual Framework for Clustering of DNA Microarray Data'' which implements specific visualizations of the data that may not be useful when using other data than DNA data. Still with this knowledge and this specific task these visualizations may prove more useful than only the once targeted at the general use-case of clustering. There are various examples for domains in which such specific frameworks exist, even for the task of clustering ``Memes'' \cite{Dang2017} to detect emerging events and topics driven by rumours, a framework has been created.

\subsection{other Visual Frameworks}
